### 2017-09-06 monograph/thesis/chapters/introduction.tex
Renamed the chapthers{1,2}.tex to introduction.tex and
implementation.tex

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for discoursing. So in this
    work implementation tool called ``Object Beautifier'' specifically dedicates on how to perform
    the best layout/display of programming code on the computer screen, so that maximize and
    facilitate the understanding of same. Therefore, allowing the programmer to disperse more tempe
    thinking about its coding algorithms problem, other than trying to decipher the information that
    is presented to it on the screen through infinit different code layouts.

>>>>

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for discoursing. So in this
    work implementation tool called `Object Beautifier' specifically dedicates on how to perform
    the best layout/display of programming code on the computer screen, so that maximize and
    facilitate the understanding of same. Therefore, allowing the programmer to disperse more tempe
    thinking about its coding algorithms problem, other than trying to decipher the information that
    is presented to it on the screen through infinit different code layouts.
